Spin canonical rings of log stacky curves

### 2016-01-05 curves-write-up/spin-cring.tex

\noindent
Let $\sx$ be a stacky curve with coarse space $X$.
If $D \in \di \sx$ is a Weil divisor, then we define
\begin{align*}
	H^0(\sx, D) &:= H^0(X, \lfloor D \rfloor)\\
	H^0(\sx, \sco(D)) &:= H^0(\sx, D)\\
	h^0(\sx, \sco(D)) &:= \dim_\Bk H^0(\sx, \sco(D))
\end{align*}
If $R$ is a graded ring, then we let $(R)_k$ refer to the $k^\text{th}$
graded component of $R$.

\end{defn}

@@

\begin{figure}
\includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
\caption{This figure shows each non-negative best lower approximation of $\frac{14}{5}.$ Each ``$\bullet$'' denotes a best lower approximation and each ``$\circ$'' denotes a lattice point below $5y=14x$ which is not a best lower approximation.  Note that the non-negative best lower approximations generate the monoid of lattice points in the first quadrant satisfying  $5y \le 14x$, with the operation $(a_1, b_1)(a_2, b_2)\mapsto (a_1 + a_2, b_1 + b_2)$ .}\label{fig:s14/5-lattice}
\end{figure}
\todo{Is this figure (figure 1)  still useful anywhere?}

>>>>

\noindent
Let $\sx$ be a stacky curve with coarse space $X$.
If $D \in \di \sx$ is a Weil divisor, then we define
\begin{align*}
	H^0(\sx, D) &:= H^0(X, \lfloor D \rfloor)\\
	H^0(\sx, \sco(D)) &:= H^0(\sx, D)\\
	h^0(\sx, \sco(D)) &:= \dim_\Bk H^0(\sx, \sco(D))
\end{align*}
If $R$ is a graded ring, then we let $(R)_k$ refer to the $k^\text{th}$
graded component of $R$.
\end{defn}

\begin{rem}
\label{rem:gorenstein}
	The log canonical ring, defined to be the direct sum of the even
	graded pieces of the log spin canonical ring, is Gorenstein. It is
	Cohen--Macaulay from \cite[Example 2.5(a)]
	{watanabe:demazure-normal-graded} and then Gorenstein by
	\cite[Corollary 2.9]{watanabe:demazure-normal-graded}. In
	particular, this tells us that a log spin canonical curve, the
	projectivization of a log spin canonical ring, is projectively
	Gorenstein.
\end{rem}

@@

%\begin{figure}
%\includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
%\caption{This figure shows each non-negative best lower approximation of $\frac{14}{5}.$ Each ``$\bullet$'' denotes a best lower approximation and each ``$\circ$'' denotes a lattice point below $5y=14x$ which is not a best lower approximation.  Note that the non-negative best lower approximations generate the monoid of lattice points in the first quadrant satisfying  $5y \le 14x$, with the operation $(a_1, b_1)(a_2, b_2)\mapsto (a_1 + a_2, b_1 + b_2)$ .}\label{fig:s14/5-lattice}
\end{figure}
%\todo{Is this figure (figure 1)  still useful anywhere?}
